The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
scale methods

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types at 30x30m resolution. We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat. Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.

@@

#### Landcover scale

Sample same landcover product at different scales. Landcover is the Fogo landcover product. Resampled using `grainchanger` from regular resolution (believe it's 30m), to 100m, 250m, 500m, 1000m, 2500m (tentative numbers). Resampling method was modal moving window. Water areas were masked before resampling. Landcover reclassified to open, forest and lichen.

>>>>

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types at 30 x 30m resolution. We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat. Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.

@@

#### Altering landcover scale

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the **`grainchanger` package[???]** at five scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). represents the local foraging Resampling method was modal moving window. Water areas were masked before resampling. Landcover reclassified to open, forest and lichen.
